The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

To this end, this work introduces a dense thin disc of ISM\
around a jet source to deflects and decelerates the oblique jets,\
in an attempt to resolve the symmetry problem of the Galactic bubbles.\

@@

  With the recourse to the isothermal and hydrostatic equilibrium conditions,\
  and assuming the interfaces between isothermal disc and atmosphere are in thermal pressure equilibrium,\
  we can write the steady-state gaseous density distribution,\
  confined in the total potential, of the disc and the Galactic atmosphere as\
  \begin{subequations}
  \begin{align}
     \displaystyle \rho_{\text{isoDisk}}(z) = \rho_{\text{isoDisk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disc-density}\\
     \text{, if $|z| < z_{0}$}& \nonumber \\
     \nonumber\\
     \displaystyle \rho_{\text{atmp}}(z) = \rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right]&\label{isothermal-atmp-density}\\
     \text{, otherwise,}& \nonumber
  \end{align}
  \label{disc-atm-sys}
  \end{subequations}
  where $m_{\text{p}}$ is the proton mass,\
  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disc and atmosphere,\
  $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disc and atmosphere on the mid-plane $z=0$.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
    \caption{The density profile of the isothermal disc (red pluses) and\
             atmosphere (blue crosses) along the positive z-axis.\
             The density distribution is derived from hydrostatic equilibrium,\
             the interface ($z=0.1$) between the isothermal disc\
             and the atmosphere is pressure balanced.}
    \label{fig__initial-density-profile}
  \end{figure}

@@

  pyFC randomly generates dimensionless 3D scalar field $f(\bold{x})$\ % that is clumpy and porous.
  that obeys the log-normal probability distribution\
  with mean $\mu$ and dispersion $\sigma$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power-law index $\beta=5/3$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disc,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
  for constructing a clumpy scalar field, and we do not repeat here.

  The density of clumpy disc can thus be obtained by taking the scalar products of\
  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disc, i.e.,\
  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
  f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
  Also, the thermal pressure equilibrium within the clumpy disc implies that the temperature of disc is
  $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
  T_{\text{isoDisk}}(z)\rho_{\text{isoDisk}}(z)/\rho_{\text{ismDisk}}(\bold{x})$.

@@

  On the basis of this setup, we cover the AMR base level with\
  $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
  based on the gradient of mass density.\
  We also restrict the refinement level at 7 within the cold disc so that\
  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.

@@

  Note that as we inject the jets at the center of the clumpy disc,\
  we define the atmosphere gas density by the peak density of\
  the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.

>>>>

To this end, this work introduces a dense, thin disc of ISM\
around a jet source to deflects and decelerates the oblique jets,\
in an attempt to resolve the symmetry problem of the Galactic bubbles.\

@@

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  and assuming the interfaces between the disc and atmosphere are in thermal pressure equilibrium,\
  we can write the steady-state gaseous density distribution,\
  confined in the total potential, of the disc and  Galactic atmosphere as\
  \begin{subequations}
  \begin{align}
     \displaystyle \rho_{\text{isoDisk}}(z) = \rho_{\text{isoDisk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disc-density}\\
     \text{, if $|z| < z_{0}$,}& \nonumber \\
     \nonumber\\
     \displaystyle \rho_{\text{atmp}}(z) = \rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right]&\label{isothermal-atmp-density}\\
     \text{, otherwise,}& \nonumber
  \end{align}
  \label{disc-atm-sys}
  \end{subequations}
  where $m_{\text{p}}$ is the proton mass,\
  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the disc and atmosphere,\
  $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disc and atmosphere on the mid-plane $z=0$.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
    \caption{The density profile of the disc (red pluses) and\
             atmosphere (blue crosses) along the positive z-axis.\
             The density distribution is derived from hydrostatic equilibrium,\
             the interface ($z=0.1$) between the isothermal disc\
             and the atmosphere is pressure balanced.}
    \label{fig__initial-density-profile}
  \end{figure}

@@

  pyFC randomly generates dimensionless 3D scalar field $f(\bold{x})$\ % that is clumpy and porous.
  that obeys the log-normal probability distribution\
  with mean $\mu$ and dispersion $\sigma$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power-law index $\beta=5/3$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within the disc,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
  for constructing a clumpy scalar field, and we do not repeat here.

  The density of the clumpy disc can thus be obtained by taking the scalar products of\
  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disc, i.e.,\
  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
  f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
  Also, the thermal pressure equilibrium within the clumpy disc implies that the temperature of the disc is
  $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
  T_{\text{isoDisk}}(z)\rho_{\text{isoDisk}}(z)/\rho_{\text{ismDisk}}(\bold{x})$.

@@

  On the basis of this setup, we cover the AMR base level with\
  $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
  based on the gradient of mass density.\
  We also restrict the refinement level at 7 within the disc so that\
  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.

@@

  Note that as we inject the jets at the center of the clumpy disc,\
  we define the atmosphere gas density by the peak density of\
  the smooth disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.
